---
title: "Food beyond land: seafood contribution to human nutrition in Brazil"
author: "Maria Luiza Gallina et al., ReefSynthesis Working Group"
date: "2025-07-03"
output: github_document
---




<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
<!-- badges: end -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Repository containing the data and scripts used in the article "Food beyond land: seafood contribution to human nutrition in Brazil", being reviewed in Nature Food.


<!-- badges: start -->
<!-- badges: end -->

## The project is organized as follows:

## **Root**

|--- **data_fisheries_nutrients**: Raw nutritional and trait data.\
|----------- "Atributos_especies_Atlantico_&_Pacifico_Oriental_2020_04_28.csv": Reef fish traits (Quimbayo et al. 2021, DOI: doi/10.1002/ecy.3298). \
|----------- "FINAL_RECONSTRUCTED_Brazil_1950_2015_CommercialEtapaII_04072021_IP_Freire.xlsx": Time series of fisheries catches (reconstructions) (Freire et al. 2021, from http://www.propesq.pesca.sp.gov.br/37/conteudo). \
|----------- "Nutrients_TBCA.xlsx": Table of nutritional content (Brazilian Table), from http://www.tbca.net.br/. \
|----------- "Species_Nutrient_Predictions.csv": data from Hicks et al. (2019), available at https://github.com/mamacneil/NutrientFishbase and https://fishbase.mnhn.fr/Nutrients/manual/FishBaseNutrients_2021_06.pdf . \
|----------- Nutrients_imputation.xlsx: List of taxa with nutritional data in some data base that were used to calculate the nutritional content of food items with missing data in RFB. For example, average nutrient values for *Penaeus*, *Penaeus esculentus*, *Penaeus latisulcatus*, *Penaeus merguiensis*, *Penaeus monodon*, *Penaeus semisulcatus* were used to input nutritional data for *Penaeus brasiliensis*. \
|----------- uFiSh1.0.xlsx: uFish nutritional data. Obtained from https://www.fao.org/infoods/infoods/tables-and-databases/faoinfoods-databases/en/. \
|----------- "Threshold_FAO.xlsx": FAO's thresholds of nutrient consumption\
\
|--- **POF_government**: Raw data (POF, or RFB in the article) from Brazilian government. The data we used is in the folder "Dados_20210304" (not visible on GitHub as it has 1.14GB size). The folder was created from data found at https://www.ibge.gov.br/estatisticas/sociais/saude/24786-pesquisa-de-orcamentos-familiares-2.html?=&t=microdados.\
|----------- "Omega3_QTD.csv": Content of Omega-3 in food. Values were gathered from FAO and FishBase. Note that values were only recorded for fish (red meat sources have Omega-3 equal to 0).\
|----------- "POP2017_20220905.xls": Brazilian population in 2017, per municipality. Data from IBGE.\
|----------- "POP2018_20220905.xls": Brazilian population in 2017, per municipality. Data from IBGE.\
|----------- "Cadastro de Produtos do Consumo Alimentar.xlsx": List of food items in POF/RFB data. Definition of animal protein items and seafood items was done based on this table. Data from POF database.\
|----------- "Pib_BR.xlsx": Gross domestic product of Brazilian states. Data from IBGE.\
\
|--- **processed_data**: Data sets obtained after processing the raw data sets.\
|----------- "POF_processed_data.RData": processed data using POF dataset hosted in the folder "POF_government". This resulted from running the R script "0_extract_POF_data.R"\
|----------- "consumption_nutrients.RData": processed data concerning the consumption of nutrients from seafood". This resulted from running the R script "2_nutrient_demand.R". This data set is used to define seafood demand.\
|----------- "consumption_nutrients_Other.RData": processed data concerning the consumption of nutrients from other sources than seafood". This resulted from running the R script "2_nutrient_demand.R"\
|----------- "fishConsumption_Income_all_food.RData": processed data concerning the consumption of nutrients from all food sources, to explore overall consumption". This resulted from running the R script "1_pof_nutrients_NUM_UC.R"\
|----------- "fishConsumption_Income_meat.RData": processed data concerning the consumption of nutrients from animal protein items, to explore overall consumption of animal protein". This resulted from running the R script "1_pof_nutrients_NUM_UC.R"\
|----------- "table_supply_state.RData": processed data concerning the catch amount per state, after matching fisheries and nutritional data. This resulted from running the R script "5_generate_nutrient_supply.R"\
|----------- "fisheries_wtrait.xlsx": Nutritional data per taxon. Obtained after matching fisheries, trait and nutritional data at the different taxonomic levels of fisheries data. This resulted from running the R script "5_generate_nutrient_supply.R"\
|----------- "state_interviewees.xlsx": Number of interviewees per state. This resulted from running the R script "1_pof_nutrients_NUM_UC.R"\
|----------- "worms_fish.RData": Taxonomic classification of fisheries and nutritional data (validation using WORMS data - worrms R package). This resulted from running the R script "5_generate_nutrient_supply.R"\
\
\
|--- **output**\
|----------- figures (pdf) and RData\
\
|--- **R**\
|----------- several R scripts (numbered according to the processing order - to reproduce results run in that order, from "0_extract_POF_data.R" to "8_supp_map_consumption_allstates.R".) \


#### This paper was produced using the following software and associated packages:

```{r pressure, echo=F,warning=F,message=F}

source("R/packages.R")
sessionInfo()


```

