---
title: "Food beyond land: seafood contribution to human nutrition in Brazil"
author: "Maria Luiza Gallina et al., ReefSynthesis Working Group"
date: "2024-06-04"
output: github_document
---




<!-- README.md is generated from README.Rmd. Please edit that file -->

<!-- badges: start -->
<!-- badges: end -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Repository containing the data and scripts used in the article "Food beyond land: seafood contribution to human nutrition in Brazil", to be submitted to Current Biology.


<!-- badges: start -->
<!-- badges: end -->

# The project is organized as follows:

Root

|--- data_fisheries_nutrients\
|----------- "Atributos_especies_Atlantico_&_Pacifico_Oriental_2020_04_28.csv": Reef fish traits (Quimbayo et al. 2021)\
|----------- "FINAL_RECONSTRUCTED_Brazil_1950_2015_CommercialEtapaII_04072021_IP_Freire.xlsx": Landings time series (Freire et al. 2021)\
|----------- "Nutrients_TBCA.xlsx": Table of nutritional content (Brazilian Table), from http://www.tbca.net.br/\
|----------- "Species_Nutrient_Predictions.csv": data from Hicks et al. (2019), available at https://github.com/mamacneil/NutrientFishbase and https://fishbase.mnhn.fr/Nutrients/manual/FishBaseNutrients_2021_06.pdf\
|----------- "Threshold_FAO.xlsx": FAO's thresholds of nutrient consumption\
\
|--- processed_data\
|----------- "POF_processed_data.RData": processed data using POF dataset hosted in the folder "POF_government". This resulted from running the R script "0_extract_POF_data.R"\
\
\
|--- output\
|----------- figures (pdf) and RData\
\
|--- POF_government\
|----------- "Omega3_QTD.csv": Content of Omega-3 in food. Values were gathered from FAO and FishBase. Note that values were only recorded for fish (red meat sources have Omega-3 equal to 0).\
\
|--- POF_state\
|----------- Brazilian government data\
\
|--- R\
|----------- several R scripts (numbered according to the processing order) \


#### This paper was produced using the following software and associated packages:

```{r pressure, echo=F,warning=F,message=F}

source("R/packages.R")
sessionInfo()


```

